|

### 2022-07-24 manuscript.Rmd
expand content delivery and closing remarks

According to LinkedIn's 2017 U.S. Emerging Jobs Report, machine learning engineers and data scientists rank among the top emerging jobs (cite).
With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula. However, a consensus on what should be included in such curricula has not yet been reached. 
In the latest version of *Computing Competencies for Undergraduate Data Science Curricula* by ACM Data Science Task Force, accessibility is a recommended content for the data science curricula [@danyluk2021computing].

@@

@@

We firmly believe that an accessible future in the field of data science requires educators to deliberately teach accessibility as part of the curriculum. 
We also acknowledge that what we have presented here is only a small portion of the intersection of visual accessibility and data science. 
One of the co-authors was supported through a Teach Access grant to develop curricular materials on teaching accessibility as part of the data science curriculum. These open-access teaching materials can be accessed at [HIDDEN FOR REVIEW].

>>>>

According to LinkedIn's 2017 U.S. Emerging Jobs Report, machine learning engineers and data scientists rank among the top emerging jobs.
With the urgent need for training a higher number of skilled data scientists, many institutes of higher education are developing their own data science curricula, and a consensus on what should be included in such curricula has not yet been reached. 
In the latest version of *Computing Competencies for Undergraduate Data Science Curricula* by ACM Data Science Task Force, accessibility is a recommended content for the data science curricula [@danyluk2021computing].

@@

Ample opportunities in learning accessibility should also include assessments. 
For instance, instructors incorporating accessibility should modify assessment instructions and rubrics to include accessibility. 
This will prevent students just hearing about accessibility in the lecture then forgetting about it. 
Ideally, the assessments should not treat accessibility as a learning objective at a single point in the academic term. 
For instance, if accessibility is covered in Week 3 of the term, students can (and should) still be expected to write alternate texts for visualizations in Week 10.

In this manuscript we have focused on domain-specific (i.e. data science) knowledge of accessibility using a particular language (R). 
Depending on the courses taught, instructors may want to extend the accessibility content to non-data contexts. 
In addition they may adopt the content in their courses with other languages such as Python and SAS or even in their language-agnostic courses. 
Overall, if taught well, a student learning accessibility content, for instance, should be able to include alternate text in their PowerPoint presentation in their Anthropology class. 
In other words, accessibility knowledge should extend beyond data science and beyond any tool.

@@

We firmly believe that an accessible future in the field of data science requires educators to deliberately teach accessibility as part of the curriculum. 
We also acknowledge that what we have presented here is only a small portion of the intersection of visual accessibility and data science. 
The second co-author was supported through a Teach Access grant to develop curricular materials on teaching accessibility as part of the data science curriculum. 
Educators interested in teaching accessibility can follow the organization's work at https://teachaccess.org/.
